brados: declarative, programmable object storage

### 2016-05-25 paper.tex
paper: add dpic
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:cls_wr_jewel}
\end{figure}
%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
%      \caption{1hr,1k,wr,jewel}
%      \label{fig:vanilla_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%      \caption{1hr,1k,rd,jewel}
%      \label{fig:vanilla_rd_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%      \caption{1hr,1k,cls\_wr,jewel}
%      \label{fig:cls_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
%      \caption{1hr,1k,wr,firefly}
%      \label{fig:vanilla_wr_firefly}
%  \end{subfigure}
%  \caption{placeholder.}
%\end{figure}

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate these contexts, we describe the 
software, system tunables, and hardware parameters that affect the performance 
of ZLog.

@@

\textbf{Ceph Versions}: to show the evolution of Ceph's performance and
behavior, we ran the same benchmark, which measures append throughput, with the
same configurations, hardware, and tunables on 2 versions of Ceph: Jewel (April
2016) - the newest stable release and Firefly (May 2014)- long term support
version that introduced cache tiering and erasure coding.
Figure~\ref{fig:jewel_v_firefly_v_es} shows the behavior and performance of the
benchmark for 128b, 1KB, and 4KB objects.

For all graphs,

That figure demonstrates that the 
bytestream interface outperforms the key-value interface by 12\%, compared to
over 100\% in the newer version of Ceph. Qualitatively, given the reduced
overall throughput achieved in the older version, some developers may find that
incurring the overhead of using the key-value interface is an easy decision
given the reduced complexity of the design space for metadata management. If
this choice had been made, then a future system upgrade could drop a
significant number of iops on the floor.

@@

@@

@@

Ceph is designed to run on a wide variety of commodity hardware as well as new
NVMe devices, all of which their own set of characteristics and tunables (e.g.,
the IO operation scheduler type). In our experiments, we tested SSD, HDDs, NVMe
devices, and

>>>>

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate these contexts, we describe the
software, system tunable, and hardware parameters that affect the performance
of our CORFU implementation. The complexity and breadth of our parameter sweep,
and the fact that our state space grew so large, motivates brados in section 4.

@@

\textbf{Ceph Versions}: to show the evolution of Ceph's performance and
behavior, we ran the same benchmark, which measures append throughput, with the
same configurations, hardware, and tunables on 2 versions of Ceph: Jewel (April
2016) - the newest stable release and Firefly (May 2014) - a long term support
version that introduced cache tiering and erasure coding. The Jewel row of 
Figure~\ref{fig:jewel_v_firefly_v_es} shows that the size of the log entries
has a clear impact on performance but the Firefly release shows no such trend.
The fact that the appends per second are an order of magnitude slower on
Firefly indicates that the the benchmark is bottlenecked by the Ceph software
instead of the external log implementation.

The bytestream interface outperforms the key-value interface by 12\%, compared
to over 100\% in the newer version of Ceph. Qualitatively, given the reduced
overall throughput achieved in the older version, some developers may find that
incurring the overhead of using the key-value interface is an easy decision
given the reduced complexity of the design space for metadata management. If
this choice had been made, then a future system upgrade could drop a
significant number of iops on the floor.

@@

\textbf{Takeway}: choosing the best implementations is dependent on both the
timing of the developemnt (Ceph Version) and the expertise of the administrator
(Ceph Features). Different versions and features of Ceph may lead the
administrator to choose a suboptimal implementation for the system's next
upgrade. The software parameters must be accounted for and benchmarked when
making design decisions.

@@

\textbf{Takeaway}: the number and complexity of Ceph's tunables make
brute-force parameter selection impossible.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:jewel-hdd-128b}
\end{figure}

Ceph is designed to run on a wide variety of commodity hardware as well as new
NVMe devices, all of which their own set of characteristics and tunables (e.g.,
the IO operation scheduler type). In our experiments, we tested SSD, HDDs, NVMe
devices and discovered a wide range of behaviors and performance profiles.
Figure~\ref{fig:jewel-hdd-128b}, which shows the write performance of 128 by
log entries using Jewel and a single HDD, shows an especially tricky situation
for a developer.

In that figure, the performance is 10\(\times\) slower than its SSD counterpart
but performance of the N:1 bystestream implementation is almost identical to
the N:1 KV implementation (within 1\% mean throughput). Regardless of the true
bottleneck, it is clear that choosing the N:1 KV implementation is the better
choice because of the simple implementation and the minimal performance
degradation.

\textbf{Takeaway}: choosing the best implementations is dependent on hardware.
Something as common as an upgrade from HDD to SSD may nullify the benefits of a
certain implementation.
